The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2019-09-10 tex/VHzQ.tex
VHzQ.tex updated

\section{Updated VH$z$Q Sample}
\label{app:qso_sample}
{\bf In the journal submitted version of this paper, as well as the
arXiv v1, we had 463 VH$z$Qs selected from the literature which we
thought was the complete sample.  However, there were 25 (twenty-five)
objects which should have been in our sample but were not (priv. comm
from Jinyi Yang and Krisztina Perger).

We downloaded Tables 2, 3 \& 4 from \cite{YangJ2018a} and found all
matches with $2\arcsec$ and added the 16 objects that had $z\geq5$;
one object from Table 3 (SUHAW J1016+2541) and 15 from Table 4, see
Table~\ref{tab:new_qsos}.

We initially downloaded the 20190514 version of the Perger
catalogue\footnote{http://astro.elte.hu/$\sim$perger/catalog.html} again
matching on a $2\arcsec$ radius. We found several objects that were in both
catalogues but had disagreement on the coordinates. Most of these were
fixed by checking the literature for the original catalogue.

There was one QSO in the Perger catalogue which could not be immediately fixed
by looking up the original coordinates in the literature: VA-13492.
In this case the coordinates looked similar to SDSSJ1040-1155, and
the stated redshift was identical, $z=5.44$. Additionally, in this case,
the $i$-band magnitude was equivalent to SDSS J1040-1155
($i=25.9$ mag), so we have decided that both of these objects are the same and 
have been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
transcription error seems to have occurred after \cite{Douglas2007} and is in
\cite{Flesch2015}, so it probably occurred in \cite{Flesch2015}.

The five objects from the submitted version of Ross \& Cross that have
changed position are in Table~\ref{tab:disagree_objs}. The
Perger catalogue has been updated to the 20190724 version (which
matches our catalogue). %%A final test of matching to with $1\arcsec$
%%found another difference: we had downloaded the OGLEJ015531-75
%%coordinates from the published paper and Perger had done so from the
%%submitted arXiv paper - and \cite{Kozlowski2019} made a minor update
%%to the positional values in between.

We exclude DES0141-54 that is in the Perger catalogue from our final
sample. This object came from a conference proceedings
\cite{Belladitta2018}, which did not have arcsecond precision in its
coordinates so we could not perform our matched-aperture photometry.
Our final catalogue has 488 $z\geq$ QSOs, see Table~\ref{tab:new_qsos}.}

%% Table New QSOs --> name, ra, dec, redshift, reference, source
%% Table QSOs in disagreement --> name, correct pos, difference, literature,
% ErrorInCR, TypeOfError

\begin{table*}   
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & redshift & reference & source  \\
\hline  
SUHAWJ1016+2541 & +154.1571250 & +25.6921944 & +5.64 &Yang2018 & Yang2018 \\
PS1J0052+4556 & +13.1810417	& +45.9422306 & +5.31 & Yang2018   & Yang2018 \\
PS1J0332+1811 & +53.1540833	& +18.1998000 & +5.12 & Yang2018   & Yang2018 \\
PS1J0511-0754 & +77.9780417	& -7.9123056 & +5.13 & Yang2018 & Yang2018 \\
PS1J0616-1338 & +94.1015833	& -13.6351111	& +5.58 & Yang2018 & Yang2018 \\
PS1J0757-0002 & +119.4412500 & -0.0336361 & +5.54 &	Yang2018 & Yang2018 \\
PS1J0817-1633 & +124.2527500 & -16.5581361 & +5.06 & Yang2018 & Yang2018 \\
PS1J1034-1233 & +158.6535833 & -12.5618028 & +5.51 & Yang2018 & Yang2018 \\
PS1J1057-1758 & +164.3650000 & -17.9754722 & +5.34 & Yang2018 & Yang2018 \\
PS1J1121-0718 & +170.4318750 & -7.3110250 & +5.71 & Yang2018 & Yang2018 \\
PS1J1137-1049 & +174.3973750 & -10.8262611 & +5.50 & Yang2018 & Yang2018 \\
PS1J1310-0639 & +197.5546250 & -6.6643222 & +5.06 & Yang2018  & Yang2018 \\
PS1J1313-2617 & +198.3585833 &-26.2893972 & +5.54 & Yang2018 & Yang2018 \\
PS1J1427-0503 & +216.8398333 & -5.0647333 & +5.08 & Yang2018 & Yang2018 \\
PS1J1533-1810 & +233.4990000 &-18.1742250 & +5.03 & Yang2018 & Yang2018 \\
PS1J2033+1218 & +308.2936250 & +12.3143028 & +5.11 & Yang2018 & Yang2018 \\
OGLEJ015531-752807 & +28.8792083 & -75.4686111 & +5.09 & Kozlowski2019 & Perger
\\
TNJ0924-2201 & +141.0830000	& -22.0281940 & +5.19 & vanBreugel1999 & Perger \\
XMMJ125329+30 & +193.3725460 & +30.9276197 & +5.08 & Khorunzhev2017 & Perger \\
SDSSJ141912.03+53 & +214.8001310 &+53.6775646 & +5.38 & Paris2017 & Perger \\
TGSSJ1530+1049 & +232.7079167 & +10.8253060	& +5.72 & Saxena2018 & Perger \\
PSOJ352.4034-15.337 & +352.4034850 & -15.3373500 & +5.84 & Banados2018 & Perger
\\
PSOJ0046-2837 & +11.5985420	& -28.6298170 & +5.99 & Venemans2018 & Perger \\
VIKJ2318-3029 & +349.6379420 & -30.4926030 & +6.1458 & Venemans2018 & Perger \\
HSC1732+6531 & +263.1796583	& +65.5204139 & +6.60 & Songaila2018 & Other \\
\hline  \hline
\end{tabular}
\caption{{\bf New QSOs added to the paper since the submitted version. }
}
\label{tab:new_qsos}
\end{table*}

%\iffalse
\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & redshift & difference \\
 & deg & deg & & arcsec  \\
\hline
%% QSOs where pos changed (same name)
DELSJ1048-0109 & +162.0795417 & -1.1611694 & 6.678 & 12.1 \\
SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & 6.04 & 150.0 \\
DELSJ1559+2212 & +239.7878750 & +22.2040083	& 6.07 & 3.0 \\
ATLASJ332.8017-32.1036 & +332.8017500 & -32.1035556	& 6.3394 &	3.2 \\
VIKJ2318-3113 & +349.5764625 & -31.2295417 & 6.4435 & 239.9 \\
\hline  \hline
\end{tabular}
\caption{{\bf QSOs where the coordinates are in  disagreement between
the submitted (arXiv v1) and accepted version of the paper.}}
\label{tab:disagree_objs}
\end{table*}
%\fi

>>>>

\section{Updated VH$z$Q Sample}
\label{app:qso_sample}
{\bf Between the journal submitted version of this paper (which was
also the arXiv v1) we updated the sample of VH$z$Qs from a total of
463 objects to 488 objects.  16 of these objects were from
\cite{YangJ2018a} and 9 objects were added after discussions with
Krisztina Perger, with the relevant catalog found
\href{http://astro.elte.hu/$\sim$perger/catalog.html}{astro.elte.hu/$\sim$perger/catalog.html}.
We do not include the object DES0141-54 \citep{Belladitta2018}, since we were unable to 
obtain arcsecond level coordinates to perform our matched-aperture photometry.
We also update the positions of five objects, see Table~\ref{tab:disagree_objs}.

One object in the Perger catalogue, VA-13492 we could not immediately cross-match. 
In this case the coordinates looked similar to SDSSJ1040-1155, and
the stated redshift was identical, $z=5.44$. Additionally the $i$-band magnitude 
was equivalent to SDSS J1040-1155
($i=25.9$ mag). SDSS J1040-1155 is first reported in \citet{Douglas2007} 
and a transcription error seems to have occurred in \citet{Flesch2015}.
}

\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
Object Name                      & R.A.               & Decl.  &  redshift  & difference \\
                                          & / deg             & / deg  &                & arcsec  \\
\hline
%% QSOs where pos changed (same name)
DELS J1048-0109               & +162.0795417 & -1.1611694        & 6.678   &     12.1 \\
SHELLQs J1429-0002          & +217.3342500 & -0.0353889        & 6.04    &  150.0 \\
DELS J1559+2212               & +239.7878750 & +22.2040083      & 6.07     &     3.0 \\
ATLAS J332.8017-32.1036 & +332.8017500 & -32.1035556      & 6.3394  &    3.2 \\
VIK J2318-3113                  & +349.5764625 & -31.2295417      & 6.4435  &  239.9 \\
\hline  \hline
\end{tabular}
\caption{
{\bf Five quasars with updated coordinates.}
}
\label{tab:disagree_objs}
\end{table*}
